Estimating migration rates for iteroparous species using kinship pairs found between populations

### 2021-06-30 latex/ms.tex
done 2.4,#6

\begin{align}
\mathbb{E}[H_{\rm HS, bet}] &= \pi_{\rm HS,bet} n_{\rm O, 1} n_{\rm O, 2} \nonumber\\
&= \frac{ 4 n_{\rm O, 1} n_{\rm O, 2} M } { N_{1} N_{2} } \label{HS-2-1}\\
&= \frac{ 4 n_{\rm O, 1} n_{\rm O, 2} m } { N_{2} },
\label{HS-2-2}
\end{align}
where $m$ indicates the migration rate satisfying $M = mN_{1}$. The observed number of HS pairs in a sample is defined by $\widetilde{H}_{\rm HS, bet}$, and $\mathbb{E}[H_{\rm HS, bet}]$ in Equation \ref{HS-2-1} is replaced by $\widetilde{H}_{\rm HS, bet}$, generating the linear estimator of $M$:

@@

To assess these probabilities, recall there must be two parents of arbitral offspring; the first probability is the sum of father-offspring and mother-offspring relationship, which can be written by $r_{\rm M}M/(r_{\rm S,1}N_{1}) + (1 - r_{\rm M})M/((1-r_{\rm S,1})N_{1})$, where $r_{\rm M}$ and $r_{\rm S,1}$ indicates sex ratio of parents in the migrants and in the whole of the population 1, respectively. Assuming $r_{\rm M} = r_{\rm S,1}$, the probability is simplified as $2M/N_{1}$. Similarly, the second probability is simplified as $2M/N_{2}$, implying the assumption of equal sex ratio in the migrants and the others. Taken together, we obtain
\begin{align}
\pi_{\rm PO,bet} &= \frac{2M}{N_{1}} \frac{M}{N_{2}} \frac{1}{M} \nonumber\\
&= \frac{2M}{N_{1}N_{2}}
\label{PO-1}
\end{align}

\begin{align}
\mathbb{E}[H_{\rm PO, bet}] &= \pi_{\rm PO,bet} n_{\rm O, 1} n_{\rm P, 2} \nonumber\\
&= \frac{ 2 n_{\rm O, 1} n_{\rm P, 2} M } { N_{1} N_{2} }
\label{PO-2}
\end{align}

\begin{align}
\widehat{M_2} &= \frac{N_{1} N_{2} \widetilde{H}_{\rm PO,bet} } {2 n_{\rm O, 1} n_{\rm P, 2} }
\label{PO-3}
\end{align}

\begin{align}
\widehat{m_2} &= \frac{N_{2} \widetilde{H}_{\rm PO,bet} } {2 n_{\rm O, 1} n_{\rm P, 2} }
\label{PO-4}
\end{align}

>>>>

\begin{align}
\mathbb{E}[H_{\rm HS, bet}] &= \pi_{\rm HS,bet} n_{\rm O, 1} n_{\rm O, 2} \nonumber\\
&= \frac{ 4 n_{\rm O, 1} n_{\rm O, 2} M } { N_{1} N_{2} } \label{HS-2-1}\\
&= \frac{ 4 n_{\rm O, 1} n_{\rm O, 2} m } { N_{2} },
\label{HS-2-2}
\end{align}
where $m$ indicates the migration rate satisfying $M = mN_{1}$. The observed number of HS pairs in a sample found between the two populations is defined by $\widetilde{H}_{\rm HS, bet}$, and $\mathbb{E}[H_{\rm HS, bet}]$ in Equation \ref{HS-2-1} is replaced by $\widetilde{H}_{\rm HS, bet}$, generating the linear estimator of $M$:

@@

The first and second probabilities are the same as the one introduced in the previous subsection, that is, $2M/N_{1}$ and $1/M$. The second probability is $M/N_{2}$ by definition. Taken together, we obtain
\begin{align}
\pi_{\rm PO,bet} &= \frac{2M}{N_{1}} \frac{M}{N_{2}} \frac{1}{M} \nonumber\\
&= \frac{2M}{N_{1}N_{2}}
\label{PO-1}
\end{align}

Let $H_{\rm PO,bet}$ be the number of PO pairs found in offspring samples of size $n_{\rm O, 1}$ and parent samples of size $n_{\rm P, 2}$. Assuming that the total number of PO pairs in the two populations is much higher than $H_{\rm PO,bet}$, the distribution is approximated by a binomial form (i.e., $H_{\rm PO,bet} \sim {\rm Binom}[\pi_{\rm PO,bet}, n_{\rm O, 1} n_{\rm P, 2}]$); thus, the theoretical expectation of $H_{\rm PO,bet}$ is
\begin{align}
\mathbb{E}[H_{\rm PO, bet}] &= \pi_{\rm PO,bet} n_{\rm O, 1} n_{\rm P, 2} \nonumber\\
&= \frac{ 2 n_{\rm O, 1} n_{\rm P, 2} M } { N_{1} N_{2} } \label{PO-2-1} \\
&= \frac{ 2 n_{\rm O, 1} n_{\rm P, 2} m } { N_{2} }
\label{PO-2-2}
\end{align}

The observed number of PO pairs in a sample is defined by $\widetilde{H}_{\rm PO, bet}$, and $\mathbb{E}[H_{\rm PO, bet}]$ in Equation \ref{HS-2-1} is replaced by $\widetilde{H}_{\rm HS, bet}$, generating the linear estimator of $M$ and $m$:
\begin{align}
\widehat{M_2} &= \frac{N_{1} N_{2} \widetilde{H}_{\rm PO,bet} } {2 n_{\rm O, 1} n_{\rm P, 2} },
\label{PO-3}
\end{align}
and
\begin{align}
\widehat{m_2} &= \frac{N_{2} \widetilde{H}_{\rm PO,bet} } {2 n_{\rm O, 1} n_{\rm P, 2} }.
\label{PO-4}
\end{align}
